Component-Based mruby Platform for IoT Devices

### 2018-02-11 ipsj/paper.tex
Remove vpath

%1
\vspace{-1mm}
\section{Introduction}
\label{sec:Introduction}
\vspace{-1mm}

@@

%2
\vspace{-1mm}
\section{System Model}
\label{sec:System Model}
\vspace{-1mm}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/SystemModel.pdf}
    \vspace{-1mm} \caption{System model of the proposed framework}
    \vspace{-2mm} \label{fig:SystemModel}
\end{figure}

\vspace{-3mm}
\subsection{TECS}
\label{sec:TECS}
\vspace{-1mm}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/component_diagram.pdf}
    \vspace{-1mm} \caption{Component Diagram}
    \vspace{-2mm} \label{fig:component}
\end{figure}

@@

\begin{description}
    \item[{\bf Signature Description}]
        The {\it signature} defines a {\it cell} interface.
        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'' e.g., sMotor (Fig.\ref{signature}).
        In TECS, to clarify the function of an interface, specifiers such as [in] and [out] are used, which represent input and output, respectively.
\begin{figure}[t]
\centering
\begin{lstlisting}
signature sMotor {
    void initializePort( [in]int32_t type );
    ER setPower( [in]int power );
    ER stop( [in] bool_t brake );
};
\end{lstlisting}
\vspace{-2mm} \caption{Signature Description}
\vspace{-2mm} \label{signature}
\end{figure}
    \item[{\bf Celltype Description}]
        The {\it celltype} defines {\it entry} ports, {\it call} ports, attributes, and variables.
        A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tCaller (Fig.\ref{celltype}).
        To define {\it entry} ports, a {\it signature}, e.g., sMotor, and an {\it entry} port name, e.g., eMotor, follow the keyword {\it entry}.
        {\it Call} ports are defined similarly.
        Attributes and variables follow the keywords {\it attr} and {\it var}, respectively.
\begin{figure}[t]
\centering
\begin{lstlisting}
celltype tCaller {
    call sMotor cMotor;
};
celltype tMotor {
    entry sMotor eMotor;
    attr { int32_t port; };
    var { int32_t currentSpeed = 0; };
};
\end{lstlisting}
\vspace{-2mm} \caption{Celltype Description}
\vspace{-2mm} \label{celltype}
\end{figure}
    \item[{\bf Build Description}]
        The build description is used to instantiate and connect {\it cell}s.
        Fig.\ref{build} shows an example of a build description.
        A {\it celltype} name and {\it cell} name, e.g., tMotor and Motor, respectively, follow the keyword {\it cell}.
        To compose {\it cell}s, a {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order.
        In Fig.\ref{build}, {\it entry} port eMotor in {\it cell} Motor is connected to {\it call} port cMotor in {\it cell} Caller.
        {\it C\_EXP} calls macros defined in C files.

\begin{figure}[t]
\centering
\begin{lstlisting}
cell tMotor Motor {
    port = C_EXP("PORT_A");
};
cell tCaller Caller {
    cMotor = Motor.eMotor;
};
\end{lstlisting}
\vspace{-2mm} \caption{Build Description}
\vspace{-2mm} \label{build}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/TECSFlow.pdf}
    \vspace{-1mm} \caption{Development flow using TECS}
    \vspace{-2mm} \label{fig:TECSFlow}
\end{figure}

@@

\vspace{-3mm}
\subsection{mruby}
\label{sec:mruby}
\vspace{-1mm}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/mruby.pdf}
    \vspace{-1mm} \caption{mruby/RiteVM mechanism}
    \vspace{-2mm} \label{fig:mruby}
\end{figure}

\vspace{-3mm}
\subsection{mruby on TECS}
\label{sec:mrubyonTECS}
\vspace{-1mm}

@@

%3
\vspace{-1mm}
\section{Proposed Framework}
\label{sec:Proposed Framework}
\vspace{-1mm}

@@

\vspace{-3mm}
\subsection{TINET+TECS}
\label{sec:TINET+TECS}
\vspace{-1mm}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/TINETHierarchyDiagram.pdf}
    \vspace{-1mm} \caption{TINET and TOPPERS/ASP3 hierarchy diagrams}
    \vspace{-2mm} \label{fig:TINETHierarchyDiagram}
\end{figure}

@@

\begin{figure}[t]
\centering
\begin{lstlisting}
signature sNicDriver {
  void start(
    [send(sNetworkAlloc),size_is(size)]
        int8_t *outputp, .., ..);
  void read(
    [receive(sNetworkAlloc),size_is(*size)]
        int8_t **inputp, .., ..);
    /* Omit: other functions */
};
\end{lstlisting}
\vspace{-1mm} \caption{Signature description of the nic driver (An example of send/receive)}
\vspace{-2mm} \label{src:SendReceive}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/DynamicConnection.pdf}
    \vspace{-1mm} \caption{Dynamic connection}
    \vspace{-2mm} \label{fig:DynamicConnection}
\end{figure}

@@

\begin{figure}[t]
\centering
\begin{lstlisting}
eAPI_accept (.., ..) {
    /* Get a descriptor of intended REP cell */
    cRepSelector_getRep(&desc, repid);
    /* Set the descriptor */
    cREP_set_descriptor(desc);
    /* Call the function of intended REP cell */
    cREP_getEndpoint();
}
\end{lstlisting}
\vspace{-1mm} \caption{Accept function (a dynamic connection example)}
\vspace{-2mm} \label{src:DynamicCcode}
\end{figure}

\vspace{-3mm}
\subsection{TLSF+TECS}
\label{sec:TLSF+TECS}
\vspace{-1mm}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/TLSF.pdf}
    \vspace{-1mm} \caption{TLSF Algorithm}
    \vspace{-2mm} \label{fig:TLSF}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/UseCase_mruby.pdf}
    \vspace{-1mm} \caption{Component description of RiteVM and TLSF+TECS}
    \vspace{-2mm} \label{fig:UseCase_mruby}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/UseCase_TINET.pdf}
    \vspace{-1mm} \caption{Fixed-size and TLSF memory allocator components}
    \vspace{-2mm} \label{fig:UseCase_TINET}
\end{figure}

@@

\vspace{-3mm}
\subsection{Use case}
\label{sec:UseCase}
\vspace{-1mm}

@@

\begin{figure}[t]
\centering
\begin{lstlisting}[language=Ruby]
begin
    io = AnalogIO.new(A0, INPUT)
    cep = TCP.new()	
    cep.accept
    loop do		
        val = io.read  
        cep.snd val.to_s + "\n"		
        RTOS.delay(1000)			
    end
rescue => e	
    puts "[ERROR]" + e
end
\end{lstlisting}
\vspace{-1mm} \caption{Example of mruby application}
\vspace{-2mm} \label{src:mruby}
\end{figure}

\vspace{-1mm}
\section{Evaluation}
\label{sec:Evaluation}
\vspace{-1mm}

@@

\begin{table}[t]
    \centering
    \vspace{-1mm} \caption{Evaluation Board Environment}
    \begin{tabular}{l|l}
        \hline\hline
        Board           &   GR-PEACH                \\
        CPU             &   Cortex-A9 RZ/A1H 400MHz \\
        Flash ROM       &   8 MB                    \\
        RAM             &   10 MB                   \\
        LAN Controller  &   LAN8710A                \\
        \hline
    \end{tabular}
    \vspace{-2mm}
    \label{tab:EvaluationBoardEnvironment}
\end{table}

\vspace{-3mm}
\subsection{Performance of TINET+TECS}
\vspace{-1mm}

@@

\begin{table}[t]
    \centering
    \vspace{-1mm} \caption{Memory consumption of TINET and TINET+TECS}
    \vspace{-1mm}
    \begin{tabular}{c|r|r|r|r}
        \hline\hline
                    &   text       &  data    &   bss      &  total     \\ \hline
        TINET       &   183.94 KB  &  5.37 KB &  132.03 KB &  322.34 KB \\
        TINET+TECS  &   170.73 KB  &  5.37 KB &  149.13 KB &  325.23 KB \\
        \hline
        \multicolumn{5}{r}{Including the application and kernel objects}
    \end{tabular}
    \vspace{-2mm}
    \label{tab:EvaluationOfMemoryConsumption}
\end{table}

@@

\begin{table}[t]
    \centering
    \vspace{-1mm} \caption{Modified code lines of CDL}
    \vspace{-1mm}
    \begin{tabular}{c|r|r|r}
        \hline\hline
                         &   Size       &   Size (-- Default) & CDL  \\ \hline
        Default          &   325.23 KB  &              0 KB   &  0 lines   \\
        I                &   305.40 KB  &       -- 19.83 KB   & 18 lines   \\
        I + I\hspace{-.1em}I &   304.12 KB  &   -- 21.10 KB   & 27 lines   \\
        I + I\hspace{-.1em}I + I\hspace{-.1em}I\hspace{-.1em}I & 303.45 KB & -- 21.77 KB  & 32 lines \\
        \hline
        \multicolumn{4}{l}{I: Remove TCP}\\
        \multicolumn{4}{l}{I\hspace{-.1em}I: Remove ICMP}\\
        \multicolumn{4}{l}{I\hspace{-.1em}I\hspace{-.1em}I: Change network buffer (Remove memory pools)}
    \end{tabular}
    \vspace{-2mm}
    \label{tab:EvaluationOfConfigurability}
\end{table}

\vspace{-3mm}
\subsection{Dynamic connection}
\vspace{-1mm}

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/ComparisonOfDynamicConnection.pdf}
    \vspace{-1mm} \caption{Component diagrams for without/with dynamic connection}
    \vspace{-2mm} \label{fig:ComparisonOfDynamicConnection}
\end{figure}

@@

% \begin{figure}[t]
%     \centering
%     \includegraphics[width=8.0cm,clip]{figure/EvaluationOfDynamicConnection.pdf}
%     \vspace{-1mm} \caption{Memory consumption in two cases (with/without dynamic connection)}
%     \vspace{-1mm} \label{fig:EvaluationOfDynamicConnection}
% \end{figure}
\begin{table}[t]
    \centering
    \vspace{-1mm} \caption{Memory consumption in two cases\\(with/without dynamic connection)}
    \vspace{-1mm}
    {\tabcolsep = 1mm
    \begin{tabular}{c|r|r|r|r}
        \hline\hline
                &  CEP:1 REP:1 & CEP:1 REP:5 & CEP:2 REP:5 & CEP:5 REP:10 \\ \hline
        without &  324.98 KB   & 325.34 KB   & 326.39 KB   & 331.68 KB   \\
        with    &  325.23 KB   & 325.32 KB   & 327.24 KB   & 330.48 KB   \\
        \hline
    \end{tabular}
    \vspace{-2mm}
    }
    \label{fig:EvaluationOfDynamicConnection}
\end{table}

\begin{table}[t]
    \centering
    \vspace{-1mm} \caption{CDL code lines of without/with dynamic connection}
    \vspace{-1mm}
    \begin{tabular}{l|r|r|r}
        \hline\hline
                     &  without  &  with  &  Diff  \\ \hline
        CEP:1 REP:1  &  344 lines     &  347 lines  &  -3 lines   \\
        CEP:1 REP:5  &  369 lines     &  367 lines  &   2 lines   \\
        CEP:2 REP:5  &  387 lines     &  382 lines  &   5 lines   \\
        CEP:5 REP:10 &  485 lines     &  445 lines  &  40 lines   \\
        \hline
    \end{tabular}
    \vspace{-2mm}
    \label{tab:EvaluationOfConfigurabilityByDynamicConnection}
\end{table}

\begin{figure}[t]
 \centering
 \begin{lstlisting}
/* without Dynamic Connection */
cell tTCPCEP TCPCEP_000 {
    cREP[0] = REP_000.eREP;
    ..
    cREP[n] = REP_00n.eREP;
};
cell tTCPCEP TCPCEP_001 {
    cREP[0] = REP_000.eREP;
    ..
    cREP[n] = REP_00n.eREP;
};
..
cell tTCPCEP TCPCEP_00n {
    cREP[0] = REP_000.eREP;
    ..
    cREP[n] = REP_00n.eREP;
};
 \end{lstlisting}
 \centering
 \begin{lstlisting}
/* with Dynamic Connection */
cell tRepSelector RepSelector {
    cREP[0] = REP_000.eREP;
    ..
    cREP[n] = REP_00n.eREP;
};
cell tTCPCEP TCPCEP_000 {
    cRepSelector = RepSelector.eRepSelector;
};
cell tTCPCEP TCPCEP_001 {
    cRepSelector = RepSelector.eRepSelector;
};
..
cell tTCPCEP TCPCEP_00n {
    cRepSelector = RepSelector.eRepSelector;
};
 \end{lstlisting}
 \vspace{-1mm} \caption{Two CDL codes (without/with dynamic connection)}
 \vspace{-2mm} \label{src:ComparisonOfCDL}
\end{figure}

@@

%5
\vspace{-1mm}
\section{Related Work}
\label{sec:Related Work}
\vspace{-1mm}

@@

%6
\vspace{-1mm}
\section{Conclusion}
\label{sec:Conclusion}
\vspace{-1mm}

@@

\vspace{-2mm}
\begin{acknowledgment}
This work was supported by JSPS KAKENHI Grant Number 15H05305.
We would like to thank Hiroaki Nagashima and Kazuaki Tanaka for supporting this research.
\end{acknowledgment}
\vspace{-2mm}

>>>>

%1
\section{Introduction}
\label{sec:Introduction}

@@

%2
\section{System Model}
\label{sec:System Model}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/SystemModel.pdf}
    \caption{System model of the proposed framework}
    \label{fig:SystemModel}
\end{figure}

\subsection{TECS}
\label{sec:TECS}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/component_diagram.pdf}
    \caption{Component Diagram}
    \label{fig:component}
\end{figure}

@@

\begin{description}
    \item[{\bf Signature Description}]
        The {\it signature} defines a {\it cell} interface.
        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'' e.g., sMotor (Fig.\ref{signature}).
        In TECS, to clarify the function of an interface, specifiers such as [in] and [out] are used, which represent input and output, respectively.
\begin{figure}[t]
\centering
\begin{lstlisting}
signature sMotor {
    void initializePort( [in]int32_t type );
    ER setPower( [in]int power );
    ER stop( [in] bool_t brake );
};
\end{lstlisting}
\caption{Signature Description}
\label{signature}
\end{figure}
    \item[{\bf Celltype Description}]
        The {\it celltype} defines {\it entry} ports, {\it call} ports, attributes, and variables.
        A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tCaller (Fig.\ref{celltype}).
        To define {\it entry} ports, a {\it signature}, e.g., sMotor, and an {\it entry} port name, e.g., eMotor, follow the keyword {\it entry}.
        {\it Call} ports are defined similarly.
        Attributes and variables follow the keywords {\it attr} and {\it var}, respectively.
\begin{figure}[t]
\centering
\begin{lstlisting}
celltype tCaller {
    call sMotor cMotor;
};
celltype tMotor {
    entry sMotor eMotor;
    attr { int32_t port; };
    var { int32_t currentSpeed = 0; };
};
\end{lstlisting}
\caption{Celltype Description}
\label{celltype}
\end{figure}
    \item[{\bf Build Description}]
        The build description is used to instantiate and connect {\it cell}s.
        Fig.\ref{build} shows an example of a build description.
        A {\it celltype} name and {\it cell} name, e.g., tMotor and Motor, respectively, follow the keyword {\it cell}.
        To compose {\it cell}s, a {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order.
        In Fig.\ref{build}, {\it entry} port eMotor in {\it cell} Motor is connected to {\it call} port cMotor in {\it cell} Caller.
        {\it C\_EXP} calls macros defined in C files.

\begin{figure}[t]
\centering
\begin{lstlisting}
cell tMotor Motor {
    port = C_EXP("PORT_A");
};
cell tCaller Caller {
    cMotor = Motor.eMotor;
};
\end{lstlisting}
\caption{Build Description}
\label{build}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/TECSFlow.pdf}
    \caption{Development flow using TECS}
    \label{fig:TECSFlow}
\end{figure}

@@

\subsection{mruby}
\label{sec:mruby}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/mruby.pdf}
    \caption{mruby/RiteVM mechanism}
    \label{fig:mruby}
\end{figure}

\subsection{mruby on TECS}
\label{sec:mrubyonTECS}

@@

%3
\section{Proposed Framework}
\label{sec:Proposed Framework}

@@

\subsection{TINET+TECS}
\label{sec:TINET+TECS}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/TINETHierarchyDiagram.pdf}
    \caption{TINET and TOPPERS/ASP3 hierarchy diagrams}
    \label{fig:TINETHierarchyDiagram}
\end{figure}

@@

\begin{figure}[t]
\centering
\begin{lstlisting}
signature sNicDriver {
  void start(
    [send(sNetworkAlloc),size_is(size)]
        int8_t *outputp, .., ..);
  void read(
    [receive(sNetworkAlloc),size_is(*size)]
        int8_t **inputp, .., ..);
    /* Omit: other functions */
};
\end{lstlisting}
\caption{Signature description of the nic driver (An example of send/receive)}
\label{src:SendReceive}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/DynamicConnection.pdf}
    \caption{Dynamic connection}
    \label{fig:DynamicConnection}
\end{figure}

@@

\begin{figure}[t]
\centering
\begin{lstlisting}
eAPI_accept (.., ..) {
    /* Get a descriptor of intended REP cell */
    cRepSelector_getRep(&desc, repid);
    /* Set the descriptor */
    cREP_set_descriptor(desc);
    /* Call the function of intended REP cell */
    cREP_getEndpoint();
}
\end{lstlisting}
\caption{Accept function (a dynamic connection example)}
\label{src:DynamicCcode}
\end{figure}

\subsection{TLSF+TECS}
\label{sec:TLSF+TECS}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/TLSF.pdf}
    \caption{TLSF Algorithm}
    \label{fig:TLSF}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/UseCase_mruby.pdf}
    \caption{Component description of RiteVM and TLSF+TECS}
    \label{fig:UseCase_mruby}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/UseCase_TINET.pdf}
    \caption{Fixed-size and TLSF memory allocator components}
    \label{fig:UseCase_TINET}
\end{figure}

@@

\subsection{Use case}
\label{sec:UseCase}

@@

\begin{figure}[t]
\centering
\begin{lstlisting}[language=Ruby]
begin
    io = AnalogIO.new(A0, INPUT)
    cep = TCP.new()	
    cep.accept
    loop do		
        val = io.read  
        cep.snd val.to_s + "\n"		
        RTOS.delay(1000)			
    end
rescue => e	
    puts "[ERROR]" + e
end
\end{lstlisting}
\caption{Example of mruby application}
\label{src:mruby}
\end{figure}

\section{Evaluation}
\label{sec:Evaluation}

@@

\begin{table}[t]
    \centering
    \caption{Evaluation Board Environment}
    \begin{tabular}{l|l}
        \hline\hline
        Board           &   GR-PEACH                \\
        CPU             &   Cortex-A9 RZ/A1H 400MHz \\
        Flash ROM       &   8 MB                    \\
        RAM             &   10 MB                   \\
        LAN Controller  &   LAN8710A                \\
        \hline
    \end{tabular}
    \label{tab:EvaluationBoardEnvironment}
\end{table}

\subsection{Performance of TINET+TECS}

@@

\begin{table}[t]
    \centering
    \caption{Memory consumption of TINET and TINET+TECS}
    \begin{tabular}{c|r|r|r|r}
        \hline\hline
                    &   text       &  data    &   bss      &  total     \\ \hline
        TINET       &   183.94 KB  &  5.37 KB &  132.03 KB &  322.34 KB \\
        TINET+TECS  &   170.73 KB  &  5.37 KB &  149.13 KB &  325.23 KB \\
        \hline
        \multicolumn{5}{r}{Including the application and kernel objects}
    \end{tabular}
    \label{tab:EvaluationOfMemoryConsumption}
\end{table}

@@

\begin{table}[t]
    \centering
    \caption{Modified code lines of CDL}
    \begin{tabular}{c|r|r|r}
        \hline\hline
                         &   Size       &   Size (-- Default) & CDL  \\ \hline
        Default          &   325.23 KB  &              0 KB   &  0 lines   \\
        I                &   305.40 KB  &       -- 19.83 KB   & 18 lines   \\
        I + I\hspace{-.1em}I &   304.12 KB  &   -- 21.10 KB   & 27 lines   \\
        I + I\hspace{-.1em}I + I\hspace{-.1em}I\hspace{-.1em}I & 303.45 KB & -- 21.77 KB  & 32 lines \\
        \hline
        \multicolumn{4}{l}{I: Remove TCP}\\
        \multicolumn{4}{l}{I\hspace{-.1em}I: Remove ICMP}\\
        \multicolumn{4}{l}{I\hspace{-.1em}I\hspace{-.1em}I: Change network buffer (Remove memory pools)}
    \end{tabular}
    \label{tab:EvaluationOfConfigurability}
\end{table}

\subsection{Dynamic connection}

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/ComparisonOfDynamicConnection.pdf}
    \caption{Component diagrams for without/with dynamic connection}
    \label{fig:ComparisonOfDynamicConnection}
\end{figure}

@@

% \begin{figure}[t]
%     \centering
%     \includegraphics[width=8.0cm,clip]{figure/EvaluationOfDynamicConnection.pdf}
%     \caption{Memory consumption in two cases (with/without dynamic connection)}
%     \label{fig:EvaluationOfDynamicConnection}
% \end{figure}
\begin{table}[t]
    \centering
    \caption{Memory consumption in two cases\\(with/without dynamic connection)}
    {\tabcolsep = 1mm
    \begin{tabular}{c|r|r|r|r}
        \hline\hline
                &  CEP:1 REP:1 & CEP:1 REP:5 & CEP:2 REP:5 & CEP:5 REP:10 \\ \hline
        without &  324.98 KB   & 325.34 KB   & 326.39 KB   & 331.68 KB   \\
        with    &  325.23 KB   & 325.32 KB   & 327.24 KB   & 330.48 KB   \\
        \hline
    \end{tabular}
    }
    \label{fig:EvaluationOfDynamicConnection}
\end{table}

\begin{table}[t]
    \centering
    \caption{CDL code lines of without/with dynamic connection}
    \begin{tabular}{l|r|r|r}
        \hline\hline
                     &  without  &  with  &  Diff  \\ \hline
        CEP:1 REP:1  &  344 lines     &  347 lines  &  -3 lines   \\
        CEP:1 REP:5  &  369 lines     &  367 lines  &   2 lines   \\
        CEP:2 REP:5  &  387 lines     &  382 lines  &   5 lines   \\
        CEP:5 REP:10 &  485 lines     &  445 lines  &  40 lines   \\
        \hline
    \end{tabular}
    \label{tab:EvaluationOfConfigurabilityByDynamicConnection}
\end{table}

\begin{figure}[t]
 \centering
 \begin{lstlisting}
/* without Dynamic Connection */
cell tTCPCEP TCPCEP_000 {
    cREP[0] = REP_000.eREP;
    ..
    cREP[n] = REP_00n.eREP;
};
cell tTCPCEP TCPCEP_001 {
    cREP[0] = REP_000.eREP;
    ..
    cREP[n] = REP_00n.eREP;
};
..
cell tTCPCEP TCPCEP_00n {
    cREP[0] = REP_000.eREP;
    ..
    cREP[n] = REP_00n.eREP;
};
 \end{lstlisting}
 \centering
 \begin{lstlisting}
/* with Dynamic Connection */
cell tRepSelector RepSelector {
    cREP[0] = REP_000.eREP;
    ..
    cREP[n] = REP_00n.eREP;
};
cell tTCPCEP TCPCEP_000 {
    cRepSelector = RepSelector.eRepSelector;
};
cell tTCPCEP TCPCEP_001 {
    cRepSelector = RepSelector.eRepSelector;
};
..
cell tTCPCEP TCPCEP_00n {
    cRepSelector = RepSelector.eRepSelector;
};
 \end{lstlisting}
 \caption{Two CDL codes (without/with dynamic connection)}
 \label{src:ComparisonOfCDL}
\end{figure}

@@

%5
\section{Related Work}
\label{sec:Related Work}

@@

%6
\section{Conclusion}
\label{sec:Conclusion}

@@

\begin{acknowledgment}
This work was supported by JSPS KAKENHI Grant Number 15H05305.
We would like to thank Hiroaki Nagashima and Kazuaki Tanaka for supporting this research.
\end{acknowledgment}
